---
title: "Clean Settlement Raw Data"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", "glue", "googledrive", "here", "janitor", "lubridate", "readxl", "stringr", "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```

## Read in the Data from Google Drive 

To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream 

```{r, warning=FALSE, message=FALSE}
# excel_sheets(here::here("6.raw_data/Settlement for Palmyra data repository.xlsx"))

data <- excel_sheets(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Settlement for Palmyra data repository.xlsx"))

tiles_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Settlement for Palmyra data repository.xlsx"), sheet = "tiles") %>% 
  clean_names()

benthic_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Settlement for Palmyra data repository.xlsx"), sheet = "tiles_benthic_corrected") %>% 
  clean_names()

coral_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Settlement for Palmyra data repository.xlsx"), sheet = "coral_recruits") %>% 
  clean_names()

```

## Explore the Data 

- check if tiles and tiles benthic corrected have same columns
- plus benthic area

### Comparing Tiles and Tiles corrected (benthic)

```{r}

col1 <- colnames(tiles_raw[1:69])
col2 <- colnames(benthic_raw[1:58])

```

They are different datasets! 

**1.Tiles**

```{r}
colnames(tiles_raw)
str(tiles_raw)

sort(unique(tiles_raw$tile_id))
sort(unique(tiles_raw$tag_id))
sort(unique(tiles_raw$site))
sort(unique(tiles_raw$deployment_time_months))
sort(unique(tiles_raw$tile_side))
sort(unique(tiles_raw$annectocyma_ann))
sort(unique(tiles_raw$turf))

```

- select columns from 1 to 69
- turf is character but should be numeric?
- deployment date and retrieval date needs to be changed to Date format. format = dd.m.yy
- rename deployment_time_month = deployment_time --> keep as categorical variable 3_13 = 3 month in 2013 and 3_14 = 3 months in 2014.
- Harmonize tile side? --> we will keep them as it is and explain each one on the metadata
- annectocyma_ann: change "No picture" to NA and turn into numeric
- turf: change "No picture" to NA and turn into numeric
- Make it long instead of wide? --> Leave data as it is to avoid any misinterpretation
- remove column x68 and x59
- What to do with the #ERROR! rows?

#### Clean the Tiles Data 

```{r}

tiles_clean <- tiles_raw %>% 
  select(1:69) %>% 
  mutate(turf = case_when(turf != "No picture" ~ turf) %>% as.numeric(.),
         deployment_date = dmy(deployment_date),
         retrival_date = dmy(retrival_date),
         tile_side = case_when(tile_side == "B-needs new pic" ~ "B",
                               T ~ tile_side),
         annectocyma_ann = case_when(annectocyma_ann != "No picture" ~ annectocyma_ann) %>%
           as.numeric(.)) %>% 
  rename(deployment_time = deployment_time_months) %>% 
  select(-x68, -x59)

```

**2. Tiles Benthic**

```{r}

colnames(benthic_raw)
str(benthic_raw)

sort(unique(benthic_raw$tile_id))
sort(unique(benthic_raw$annectocyma_ann))

```

- select columns from 1 to 58
- remove columns x47, x55, x56, x57
- annectocyma_ann: replace "no pic" with NA --> NA = no information

#### Clean the Benthic Data 

```{r}

benthic_clean <- benthic_raw %>% 
  select(1:58) %>% 
  mutate(annectocyma_ann = case_when(annectocyma_ann != "no pic" ~ annectocyma_ann)) %>% 
  select(-x47, -x55, -x56, -x57)

```

**3. Coral Recruits**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
colnames(coral_raw)
str(coral_raw)

sort(unique(coral_raw$recruit_id))
sort(unique(coral_raw$top_bottom))
sort(unique(coral_raw$tile_id))
sort(unique(coral_raw$site))
sort(unique(coral_raw$taxo_id))
sort(unique(coral_raw$diameter_caliper))
sort(unique(coral_raw$diameter_milimeter_paper))
sort(unique(coral_raw$area_tile_picture_mm2))
sort(unique(coral_raw$area_milimeter_paper))
sort(unique(coral_raw$nr_of_polyps))
sort(unique(coral_raw$estimated_height_mm))
sort(unique(coral_raw$colonized_on_top_of))
sort(unique(coral_raw$overgrown_by))
sort(unique(coral_raw$overgrowth_level))
sort(unique(coral_raw$distance_to_closest_coral_neighbour_caliper))
sort(unique(coral_raw$distance_to_neighbour_tile))


```

- need to make `taxo_id` to lowercase and standardize the spelling and format of "unknown"
- fix `diameter_caliper` and make it numeric
- fix `area_tile_picture_mm2` so that it is numeric, make unknown NA
- fix `area_milimeter_paper` so that it is numeric, make unknown NA 
- look at `nr_of_polyps`, should it be numeric or categorical?  
- fix `colonized_on_top_of`, make unknown NA 
- make `distance_to_neighbour_tile` numeric
- make `distance_to_closest_coral_neighbour_caliper` numeric

#### Clean Coral Recruits 

```{r}
coral_raw$taxo_id <- tolower(coral_raw$taxo_id)

# Fix the taxo_id column 
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "-", "")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "_", "")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "\\?", "")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown  poc or acr", "unknown poc or acr")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown acr or poc", "unknown poc or acr")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "uknown", "unknown")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknownacr", "unknown acr")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknownpoc", "unknown poc")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknownpor", "unknown por")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknownpocacr", "unknown poc or acr")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown pocacr", "unknown poc or acr")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown otheroxipora", "unknown other oxipora")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown othersmall", "unknown other small")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "othersmall", "other small")
coral_raw$taxo_id <- str_replace_all(coral_raw$taxo_id, "unknown / too small to see on pic", "unknown")

coral_clean <- coral_raw

sort(unique(coral_clean$taxo_id))
coral_clean[coral_clean == "#ERROR!"] <- NA

# Fix the diameter caliper 
coral_clean$diameter_caliper <- gsub("coral*", NA, coral_clean$diameter_caliper)
coral_clean$diameter_caliper <- as.numeric(coral_clean$diameter_caliper)

# Fix the area_tile_picture_mm2
coral_clean <- coral_clean %>% 
  mutate(area_tile_picture_mm2 = case_when(area_tile_picture_mm2 != "unknown" ~ area_tile_picture_mm2))
coral_clean$area_tile_picture_mm2 <- str_replace_all(coral_clean$area_tile_picture_mm2, " \\(fuzzy circle\\)", "")
coral_clean$area_tile_picture_mm2 <- as.numeric(coral_clean$area_tile_picture_mm2)

# Fix the area_milimeter_paper 
coral_clean$area_milimeter_paper <- gsub("unknown*", NA, coral_clean$area_milimeter_paper)
coral_clean$area_milimeter_paper <- str_replace_all(coral_clean$area_milimeter_paper, " \\(broken\\)", "")
coral_clean$area_milimeter_paper <- as.numeric(coral_clean$area_milimeter_paper)

# Fix nr of polyps 
coral_clean$nr_of_polyps <- tolower(coral_raw$nr_of_polyps)
coral_clean$nr_of_polyps <- str_replace_all(coral_clean$nr_of_polyps, "uknown", "unknown")
coral_clean$nr_of_polyps <- str_replace_all(coral_clean$nr_of_polyps, "unkown", "unknown")
coral_clean$nr_of_polyps <- str_replace_all(coral_clean$nr_of_polyps, "\\?", "unknown")
coral_clean$nr_of_polyps <- gsub("unknown*", NA, coral_clean$nr_of_polyps)

# Fix colonized on top of
coral_clean$colonized_on_top_of <- tolower(coral_raw$colonized_on_top_of)
coral_clean$colonized_on_top_of <- str_replace_all(coral_clean$colonized_on_top_of, "uknown", "unknown")
coral_clean$colonized_on_top_of <- str_replace_all(coral_clean$colonized_on_top_of, "unkown", "unknown")
coral_clean$colonized_on_top_of <- gsub("unknown*", NA, coral_clean$colonized_on_top_of)

# Fix colonized on top of 2
coral_clean$colonized_on_top_of2 <- tolower(coral_raw$colonized_on_top_of2)
coral_clean$colonized_on_top_of2 <- gsub("unknown*", NA, coral_clean$colonized_on_top_of2)

# Fix colonized on top of 3
coral_clean$colonized_on_top_of3 <- tolower(coral_raw$colonized_on_top_of3)

# Fix distance to neighbor tile 
coral_clean$distance_to_neighbour_tile[coral_clean$distance_to_neighbour_tile == "NA"] <-
  NA
coral_clean$distance_to_neighbour_tile <-
  as.numeric(coral_clean$distance_to_neighbour_tile)

# Fix distance to closest caliper
coral_clean$distance_to_closest_coral_neighbour_caliper[coral_clean$distance_to_closest_coral_neighbour_caliper == "NA"] <- NA
coral_clean$distance_to_closest_coral_neighbour_caliper <-
  as.numeric(coral_clean$distance_to_closest_coral_neighbour_caliper)

# Fix overgrown by
coral_clean$overgrown_by <- tolower(coral_raw$overgrown_by)
coral_clean$overgrown_by <- gsub("#error!", NA, coral_clean$overgrown_by)
coral_clean$overgrown_by <- str_replace_all(coral_clean$overgrown_by, "\\?", "")
sort(unique(coral_clean$overgrown_by))

# Fix overgrowth level
coral_clean$overgrowth_level <- tolower(coral_raw$overgrowth_level)
coral_clean$overgrowth_level <- str_replace_all(coral_clean$overgrowth_level, "\\?", "")
sort(unique(coral_clean$overgrowth_level))


```





## Save the Clean Data 

Use this code chunk to upload the cleaned data directly to google drive. You write the file directly to the drive as if you were saving it to a local file 

```{r}
# You can use write_csv or any other function like that to write directly to the drive. 

# Example below: 
write_csv(tiles_clean, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_palmyra_settlement_tiles_2013_2014.csv"))


write_csv(benthic_clean, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_palmyra_settlement_benthic_coverage_2013_2014.csv"))

write_csv(coral_clean, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_palmyra_settlement_coral_recruits_2013_2014.csv"))

```



