---
title: "Exploring Bioerosion Data"
author: "Paloma Cartwright"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", "glue", "googledrive", "here", "janitor", "lubridate", "readxl", "stringr", "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```


## Read in the Data from Google Drive 

To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream 

```{r, warning=FALSE, message=FALSE}
# excel_sheets(here::here("6.raw_data/Bioerosion Palmyra data repository.xlsx"))

bio_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Bioerosion Palmyra data repository.xlsx"), sheet = "fungia pieces 15 month") %>% 
  clean_names()

nr_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Bioerosion Palmyra data repository.xlsx"), sheet = "nr of fungia pieces per site") %>% 
  clean_names()

reef_raw <- read_excel(glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/updated sheets with meta data/Bioerosion Palmyra data repository.xlsx"), sheet = "reef pieces ") %>% 
  clean_names()

```

## Explore

**1. fungia pieces 15 month**
```{r}
str(bio_raw)
complete(bio_raw)

sort(unique(bio_raw$fungia_id))
sort(unique(bio_raw$site))

```

- data looks pretty clean and no issues with numeric values
- Remove unit from `area_of_fungia_piece_before_deployment_mm2` and `perimeter_fungia_piece_mm`
- Why are there NAs in area and perimeter columns? 

**2. nr of fungia pieces per site**
```{r}
str(nr_raw)
complete(nr_raw)
```

- Need to add colnames: `site` and `n`

**3. reef pieces**

```{r}
str(reef_raw)
complete(reef_raw)

sort(unique(reef_raw$site))
sort(unique(reef_raw$other_calcifiers_outside))
sort(unique(reef_raw$coral))

```

- Change ? for NA in `coral`

## Clean- up

**1. fungia pieces 15 month**
Remove unit from `area_of_fungia_piece_before_deployment_mm2` and `perimeter_fungia_piece_mm`
```{r}

bio_clean <- bio_raw %>% 
  rename(area_of_fungia_piece_before_deployment = area_of_fungia_piece_before_deployment_mm2,
         perimeter_fungia_piece = perimeter_fungia_piece_mm)

```


**2. nr of fungia pieces per site**
- add colnames: `site` and `n`

```{r}

nr_names <- c("site", "n")

colnames(nr_raw) <- nr_names
  
```

**3. reef pieces**

Change ? for NA in `coral`

```{r}
reef_clean <- reef_raw %>% 
  mutate(coral = case_when(coral != "?" ~ coral))

```


```{r}
write_csv(bio_clean, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_bioerosion_fungia.csv"))

write_csv(nr_raw, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_bioerosion_n_fungia_pieces.csv"))

write_csv(reef_clean, glue("{dir_gdrive}/DATA_RAW/Franziska Elmer/clean_data/elmer_bioerosion_reef.csv") )
```


