---
title: "Cleans Calsification Data"
author: "Camila Vargas"
date: "2/16/2022"
output: html_document
---
Franziska Elmer's data.
Data on the amount of CaCO3 deposited on settlement tiles deployed up to 15 months on the reef

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load packages
library(here)
library(tidyverse)
library(janitor)
library(readxl)
library(freeR)
library(lubridate)

## Sets R not to use scientific notations
options(scipen=999) 

```

## Datasets
```{r}

excel_sheets(here::here("6.raw_data/Calcification Palmry data repository.xlsx"))

```


We need all sheets except metadata sheet.

## Read data

```{r}
bleach_raw <- read_excel(here::here("6.raw_data/Calcification Palmry data repository.xlsx"), sheet = " bleaching tiles") %>% 
  clean_names()

acid_raw <- read_excel(here::here("6.raw_data/Calcification Palmry data repository.xlsx"), sheet = "acid tiles") %>% 
  clean_names()


benthic_raw <- read_excel(here::here("6.raw_data/Calcification Palmry data repository.xlsx"), sheet = "benthic data") %>% 
  clean_names()

```


## Explore and clean

**1. Bleaching tiles**

```{r}
colnames(bleach_raw)
str(bleach_raw)

sort(unique(bleach_raw$tile_id))
sort(unique(bleach_raw$site))
sort(unique(bleach_raw$comments))

bleach_clean <- bleach_raw %>% 
  rename(organic_mater = organic_mater_g,
         initial_weight_w_bag = initial_weight_with_plastic_bag,
         bag_weight = weight_of_plastic_bag,
         weight_after = weight_after_6_days,
         notes = comments)

colnames(bleach_clean)
str(bleach_clean)

```

- remove unit from organic_mater_g

**2.Acid tiles**
```{r}
colnames(acid_raw)
str(acid_raw)

sort(unique(acid_raw$tile_id))
sort(unique(acid_raw$site))
sort(unique(acid_raw$time_deployed))
sort(unique(acid_raw$time_retrieved))
sort(unique(acid_raw$debris_acid_20ml_g))

## this works as the opposite of %in%!!
`%notin%` <- Negate(`%in%`)

acid_clean <- acid_raw %>% 
  rename(notes = x17,
         ca_co3 = kg_ca_co3_m_2_yr_1,
         debris_acid = debris_acid_20ml_g,
         tile_weight_after = x48_hrs,
         initial_weight_w_bag = initial_weight_with_plastic_bag,
         bag_weight = weight_of_plastic_bag,
         acid_volume_end = volume_of_acid_at_end_ml,
         total_debris_acid = total_debris_in_acid,
         debris_filter_weight = all_debris_filter_weight) %>% 
  mutate(deployment_date = dmy(time_deployed),
         retrival_date =  dmy(time_retrieved),
         notes = case_when(debris_acid %in% c("all acid filtered","combined with other, check which") ~ debris_acid,
                           T ~ notes),
         debris_acid = case_when(debris_acid %notin% c("all acid filtered","combined with other, check which") ~ debris_acid),
         debris_acid = as.numeric(debris_acid)) %>% 
  select(tile_id, site, deployment_date, retrival_date, everything()) %>% 
  select(-x14, -time_deployed, -time_retrieved)
  
colnames(acid_clean)
str(acid_clean)

```

- remove columns x14
- rename notes = x17
- remove unites from: kg_ca_co3_m_2_yr_1, debris_acid_20ml_g
- time_deployed and time_retrieved are Dates. format = "dd.mm.yyyy"
- debris_acid_20ml_g: move "all acid filtered" and "combined with other, check which" to notes
- make acid_debrief numeric


**3.Benthic data**
```{r}
colnames(benthic_raw)
str(benthic_raw)
complete(benthic_raw)

sort(unique(benthic_raw$tile_id))
sort(unique(benthic_raw$tag_id))
sort(unique(benthic_raw$site))
sort(unique(benthic_raw$deployment_date))
sort(unique(benthic_raw$retrival_date))
sort(unique(benthic_raw$tile_side))

benthic_clean <- benthic_raw %>% 
  mutate(deployment_date = dmy(deployment_date),
         retrival_date = dmy(retrival_date))

colnames(benthic_clean)
str(benthic_clean)

```

- deployment_date and retrival_date need to be class Date. format = "dd.m.yy"


## Saving Data

```{r}
## Bleach

write_csv(bleach_clean, here::here("7.clean_data/elmer_palmyra_bleaching_tiles_calcification_data_2013.csv"))

## Acid

write_csv(acid_clean, here::here("7.clean_data/elmer_palmyra_acid_tiles_calcification_data_2013_2014.csv"))

## Benthic
write_csv(benthic_clean, here::here("7.clean_data/elmer_palmyra_benthic_coverage_calcification_data_2013_2014.csv"))
```


