---
title: "Exploring Bioerosion Data"
author: "Camila Vargas"
date: "2/8/2022"
output: html_document
---

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load packages
library(here)
library(tidyverse)
library(janitor)
library(readxl)
library(freeR)

## Sets R not to use scientific notations
options(scipen=999) 

```

## Exploring data
```{r}

excel_sheets(here::here("6.raw_data/Bioerosion Palmyra data repository.xlsx"))

```

We want all sheets expect for Meta data. We will use the metadata to fill in the Metadata.doc


## Read Data
```{r}

bio_raw <- read_excel(here::here("6.raw_data/Bioerosion Palmyra data repository.xlsx"), sheet = "fungia pieces 15 month") %>% 
  clean_names()

nr_raw <- read_excel(here::here("6.raw_data/Bioerosion Palmyra data repository.xlsx"), sheet = "nr of fungia pieces per site") %>% 
  clean_names()

reef_raw <- read_excel(here::here("6.raw_data/Bioerosion Palmyra data repository.xlsx"), sheet = "reef pieces ") %>% 
  clean_names()

```


## Explore

**1. fungia pieces 15 month**
```{r}
str(bio_raw)
complete(bio_raw)

sort(unique(bio_raw$fungia_id))
sort(unique(bio_raw$site))

```

- data looks pretty clean and no issues with numeric values
- Remove unit from `area_of_fungia_piece_before_deployment_mm2` and `perimeter_fungia_piece_mm`
- Why are there NAs in area and perimeter columns? 


**2. nr of fungia pieces per site**
```{r}
str(nr_raw)
complete(nr_raw)
```

- Need to add colnames: `site` and `n`


**3. reef pieces**

```{r}
str(reef_raw)
complete(reef_raw)

sort(unique(reef_raw$site))
sort(unique(reef_raw$other_calcifiers_outside))
sort(unique(reef_raw$coral))

```

- Change ? for NA in `coral`



