---
title: "Cleans Settlement Data"
author: "Camila Vargas"
date: "2/17/2022"
output: html_document
---

Franziska Elmer's data.
Data showing what was found on settlement tiles deployed on the reef. Coral recruits were found with the microscope, other substrate was determined using CPCe.

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load packages
library(here)
library(tidyverse)
library(janitor)
library(readxl)
library(freeR)
library(lubridate)

## Sets R not to use scientific notations
options(scipen=999) 

```

## Datasets
```{r}

excel_sheets(here::here("6.raw_data/Settlement for Palmyra data repository.xlsx"))

```

- check if tiles and tiles benthic have same columns
- plus coral_recruits

## Read data

```{r}
tiles_raw <- read_excel(here::here("6.raw_data/Settlement for Palmyra data repository.xlsx"), sheet = "tiles") %>% 
  clean_names()

benthic_raw <- read_excel(here::here("6.raw_data/Settlement for Palmyra data repository.xlsx"), sheet = "tiles benthic corrected") %>% 
  clean_names()


coral_raw <- read_excel(here::here("6.raw_data/Settlement for Palmyra data repository.xlsx"), sheet = "coral_recruits") %>% 
  clean_names()

```


## Comparing Tiles and Tiles corrected (benthic)

```{r}
col1 <- colnames(tiles_raw[1:69])
col2 <- colnames(benthic_raw[1:58])
```

They are different datasets!

## Explore and clean

**1.Tiles**

```{r}
colnames(tiles_raw)
str(tiles_raw)

sort(unique(tiles_raw$tile_id))
sort(unique(tiles_raw$tag_id))
sort(unique(tiles_raw$site))
sort(unique(tiles_raw$deployment_time_months))
sort(unique(tiles_raw$tile_side))
sort(unique(tiles_raw$annectocyma_ann))
sort(unique(tiles_raw$turf))

tiles_clean <- tiles_raw %>% 
  select(1:69) %>% 
  mutate(turf = case_when(turf != "No picture" ~ turf) %>% as.numeric(.),
         deployment_date = dmy(deployment_date),
         retrival_date = dmy(retrival_date),
         tile_side = case_when(tile_side == "B-needs new pic" ~ "B",
                               T ~ tile_side),
         annectocyma_ann = case_when(annectocyma_ann != "No picture" ~ annectocyma_ann) %>% as.numeric(.)) %>% 
  rename(deployment_time = deployment_time_months) %>% 
  select(-x68, - x59)


```
- select columns from 1 to 69
- turf is character but should be numeric?
- deployment date and retrieval date needs to be changed to Date format. format = dd.m.yy
- rename deployment_time_month = deployment_time --> keep as categorical variable 3_13 = 3 month in 2013 and 3_14 = 3 months in 2014.
- Harmonize tile side? --> we will keep them as it is and explain each one on the metadata
- annectocyma_ann: change "No picture" to NA and turn into numeric
- turf: change "No picture" to NA and turn into numeric
- Make it long instead of wide? --> Leave data as it is to avoid any misinterpretation
- remove column x68 and x59

**2. Tiles Benthic**

```{r}

colnames(benthic_raw)
str(benthic_raw)

sort(unique(benthic_raw$tile_id))
sort(unique(benthic_raw$annectocyma_ann))

benthic_clean <- benthic_raw %>% 
  select(1:58) %>% 
  mutate(annectocyma_ann = case_when(annectocyma_ann != "no pic" ~ annectocyma_ann)) %>% 
  select(-x47, -x55, -x56, -x57)


```

- select columns from 1 to 58
- remove columns x47, x55, x56, x57
- annectocyma_ann: replace "no pic" with NA --> NA = no information


**3. Coral Recruits**
```{r}
colnames(coral_raw)
str(coral_raw)

sort(unique(coral_raw$recruit_id))
sort(unique(coral_raw$top_bottom))
sort(unique(coral_raw$tile_id))
sort(unique(coral_raw$site))
sort(unique(coral_raw$taxo_id))
sort(unique(coral_raw$diameter_caliper))
sort(unique(coral_raw$area_tile_picture_mm2))
sort(unique(coral_raw$area_milimeter_paper))
sort(unique(coral_raw$nr_of_polyps))

sort(unique(coral_raw))


coral_clean <- coral_raw %>% 
  select(1:26, -x14, -x15, x19)


```

- select columns form 1:26
- remove columns x14 and x15


## Check clean!
Need to check if all clean data is correct! And save again if necesary.


## Save clean
```{r}
## tiles
write_csv(tiles_clean, here::here("7.clean_data/elmer_palmyra_settlement_tiles_2013_2014.csv"))

## benthic
write_csv(tiles_clean, here::here("7.clean_data/elmer_palmyra_settlement_benthic_coverage_2013_1014.csv"))



##
write_csv(tiles_clean, here::here("7.clean_data/elmer_palmyra_settlement_coral_recruits_2013_2014.csv"))

```

